Framing active school travel in Ontario, or how spinach is good for you

### 2024-01-10 AST-Framing-Ontario/AST-Framing-Ontario.Rmd
Minor fixes to bibliography and text

In Ontario, municipalities, school boards and transportation consortia do not consistently include AST in their public communications. Indeed, as noted above, less than 50% of documents from these organizations discuss AST.  Interpretation of the text assisted by natural language processing reveals that when AST is discussed, the primary frame emphasizes its benefits to the health and wellbeing of both children and the environment. In the rest of the documents, the primary way AST is framed tends to emphasize the benefits to the health and wellbeing of children and to the environment. The policy documents reflect the evidence that AST contributes positively to children's physical health [see @faulknerActiveSchoolTransport2009; @schoeppeAssociationsChildrenActive2015], although the statements regarding the benefits of AST to children's school performance are less well-supported in the extant literature [@westmanTravelChildWellbeing2020]. STP stakeholder groups also communicate that increasing AST may reduce traffic near and around schools. This is conveyed presumably to alleviate parental concerns about traffic and safety [@eversParentSafetyPerceptions2014; @mammenUnderstandingDriveEscort2012; @rothmanAssociationsParentsPerception2015; @wilsonUnderstandingChildParent2018] or to reduce the frequency of risky behaviors from drivers around schools [@rothmanSchoolEnvironmentStudent2017].

@@

In terms of future research, we suggest the need for further investigation into how parents or the general public respond to messages or information that encourages the adoption of AST and evaluate which are most effective. It would be helpful to understand which frames would most encourage behavior change or increase political support for interventions that address barriers to AST. This type of information could ensure that educational strategies and promotional materials increase buy-in for their target audience. If Canadian STP stakeholders wish to involve more local residents in their efforts [@buttazzoniSupportingActiveSchool2018], it would also be worthwhile for them to produce different materials that communicate why this issue is important to the general public, regardless of whether they currently have children commuting to/from school. A difficulty when thinking about effective frames is, as an anonymous peer-reviewer insisted, demonstrating that a given strategy for communicating policy is "good value for money". It is perhaps the case that half of all the money spent in communications is wasted but, as Wanamaker quiped, it is seldom clear which half. We are not aware of any studies that try to assess the cost-effectiveness of different frames, and we suggest that this might be a fruitful area for future research in controlled settings, for example using stated preference experiments.

>>>>

In Ontario, municipalities, school boards and transportation consortia do not consistently include AST in their public communications. Indeed, as noted above, less than 50% of documents from these organizations discuss AST.  Interpretation of the text assisted by natural language processing reveals that when AST is discussed, the primary frame emphasizes its benefits to the health and wellbeing of both children and the environment. The policy documents reflect the evidence that AST contributes positively to children's physical health [see @faulknerActiveSchoolTransport2009; @schoeppeAssociationsChildrenActive2015], although the statements regarding the benefits of AST to children's school performance are less well-supported in the extant literature [@westmanTravelChildWellbeing2020]. STP stakeholder groups also communicate that increasing AST may reduce traffic near and around schools. This is conveyed presumably to alleviate parental concerns about traffic and safety [@eversParentSafetyPerceptions2014; @mammenUnderstandingDriveEscort2012; @rothmanAssociationsParentsPerception2015; @wilsonUnderstandingChildParent2018] or to reduce the frequency of risky behaviors from drivers around schools [@rothmanSchoolEnvironmentStudent2017].

@@

In terms of future research, we suggest the need for further investigation into how parents or the general public respond to messages or information that encourages the adoption of AST and evaluate which are most effective. It would be helpful to understand which frames would most encourage behavior change or increase political support for interventions that address barriers to AST. This type of information could ensure that educational strategies and promotional materials increase buy-in from their target audience. If Canadian STP stakeholders wish to involve more local residents in their efforts [@buttazzoniSupportingActiveSchool2018], it would also be worthwhile for them to produce different materials that communicate why this issue is important to the general public, regardless of whether they currently have children commuting to/from school. A difficulty when thinking about effective frames is, as an anonymous peer-reviewer insisted, demonstrating that a given strategy for communicating policy is "good value for money". It is perhaps the case that half of all the money spent in communications is wasted but, as Wanamaker quiped, it is seldom clear which half. We are not aware of any studies that try to assess the cost-effectiveness of different frames, and we suggest that this might be a fruitful area for future research in controlled settings, for example using stated preference experiments.

### 2024-01-10 AST-Framing-Ontario/AST-Framing-Ontario.tex
Minor fixes to bibliography and text

In Ontario, municipalities, school boards and transportation consortia
do not consistently include AST in their public communications. Indeed,
as noted above, less than 50\% of documents from these organizations
discuss AST. Interpretation of the text assisted by natural language
processing reveals that when AST is discussed, the primary frame
emphasizes its benefits to the health and wellbeing of both children and
the environment. In the rest of the documents, the primary way AST is
framed tends to emphasize the benefits to the health and wellbeing of
children and to the environment. The policy documents reflect the
evidence that AST contributes positively to children's physical health
\citep[see][]{faulknerActiveSchoolTransport2009, schoeppeAssociationsChildrenActive2015},
although the statements regarding the benefits of AST to children's
school performance are less well-supported in the extant literature
\citep{westmanTravelChildWellbeing2020}. STP stakeholder groups also
communicate that increasing AST may reduce traffic near and around
schools. This is conveyed presumably to alleviate parental concerns
about traffic and safety
\citep{eversParentSafetyPerceptions2014, mammenUnderstandingDriveEscort2012, rothmanAssociationsParentsPerception2015, wilsonUnderstandingChildParent2018}
or to reduce the frequency of risky behaviors from drivers around
schools \citep{rothmanSchoolEnvironmentStudent2017}.

@@

In terms of future research, we suggest the need for further
investigation into how parents or the general public respond to messages
or information that encourages the adoption of AST and evaluate which
are most effective. It would be helpful to understand which frames would
most encourage behavior change or increase political support for
interventions that address barriers to AST. This type of information
could ensure that educational strategies and promotional materials
increase buy-in for their target audience. If Canadian STP stakeholders
wish to involve more local residents in their efforts
\citep{buttazzoniSupportingActiveSchool2018}, it would also be
worthwhile for them to produce different materials that communicate why
this issue is important to the general public, regardless of whether
they currently have children commuting to/from school. A difficulty when
thinking about effective frames is, as an anonymous peer-reviewer
insisted, demonstrating that a given strategy for communicating policy
is ``good value for money''. It is perhaps the case that half of all the
money spent in communications is wasted but, as Wanamaker quiped, it is
seldom clear which half. We are not aware of any studies that try to
assess the cost-effectiveness of different frames, and we suggest that
this might be a fruitful area for future research in controlled
settings, for example using stated preference experiments.

>>>>

In Ontario, municipalities, school boards and transportation consortia
do not consistently include AST in their public communications. Indeed,
as noted above, less than 50\% of documents from these organizations
discuss AST. Interpretation of the text assisted by natural language
processing reveals that when AST is discussed, the primary frame
emphasizes its benefits to the health and wellbeing of both children and
the environment. The policy documents reflect the evidence that AST
contributes positively to children's physical health
\citep[see][]{faulknerActiveSchoolTransport2009, schoeppeAssociationsChildrenActive2015},
although the statements regarding the benefits of AST to children's
school performance are less well-supported in the extant literature
\citep{westmanTravelChildWellbeing2020}. STP stakeholder groups also
communicate that increasing AST may reduce traffic near and around
schools. This is conveyed presumably to alleviate parental concerns
about traffic and safety
\citep{eversParentSafetyPerceptions2014, mammenUnderstandingDriveEscort2012, rothmanAssociationsParentsPerception2015, wilsonUnderstandingChildParent2018}
or to reduce the frequency of risky behaviors from drivers around
schools \citep{rothmanSchoolEnvironmentStudent2017}.

@@

In terms of future research, we suggest the need for further
investigation into how parents or the general public respond to messages
or information that encourages the adoption of AST and evaluate which
are most effective. It would be helpful to understand which frames would
most encourage behavior change or increase political support for
interventions that address barriers to AST. This type of information
could ensure that educational strategies and promotional materials
increase buy-in from their target audience. If Canadian STP stakeholders
wish to involve more local residents in their efforts
\citep{buttazzoniSupportingActiveSchool2018}, it would also be
worthwhile for them to produce different materials that communicate why
this issue is important to the general public, regardless of whether
they currently have children commuting to/from school. A difficulty when
thinking about effective frames is, as an anonymous peer-reviewer
insisted, demonstrating that a given strategy for communicating policy
is ``good value for money''. It is perhaps the case that half of all the
money spent in communications is wasted but, as Wanamaker quiped, it is
seldom clear which half. We are not aware of any studies that try to
assess the cost-effectiveness of different frames, and we suggest that
this might be a fruitful area for future research in controlled
settings, for example using stated preference experiments.
